Notes on 10d Super Yang-Mills

### 2019-03-01 10d_SYM_Notes.tex
Starting SUSY transformations in 10d

\subsection{On-Shell Supersymmetry Action}
%Failure to commute with the classical BV differential

>>>>

\subsection{On-Shell Supersymmetry Action}
We can define an action of the 10d $\mc N=1$ supersymmetry algebra on the complex of BRST fields in this minimal super Yang-Mills theory.  The Poincar\'e action is clear, and the action of the supersymmetry $Q$ is generated -- in the usual Physics notation -- by the transformation \cite{BrinkSchwarzScherk}
\begin{align*}
\delta_Q A &= \Gamma(Q,\lambda) \\
\delta_Q \lambda &= \frac 14 \sd F_A Q,
\end{align*}
where the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F^{ij} \gamma_i \gamma_j$.  To check that this defines a supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra.  So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= \frac 14 (\Gamma(Q_2,\sd F_A Q_1) - \Gamma(Q_1,\sd F_A Q_2)) \\
&= \\
\text{and } \delta_{Q_1}, \delta_{Q_2}] \lambda &= \frac 14 (\sd F_{\Gamma(Q_2, \lambda)} Q_1 - \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= 
\end{align*}

%Failure to commute with the classical BV differential
